Implementing simplified INLA into `aghq`

### 2022-10-19 src/dev_sinla/sinla.Rmd
Start trying to normalise p_LA(theta | y); and add conditional mean of multivariate Gaussian

@@

In Section \@ref(full-laplace) we directly calculate the Laplace approximation to $\int p(x, y, \theta) \text{d} \theta_{-i}$.
Following Wood (2019), a cheaper approach would be to "base the denominator of Equation \@ref(eq:pxigiventhetay) on the conditional density implied by ? in which case the Hessian is constant and
$$
\mu(x_i, \theta) = \mu(\theta) + \Sigma(\theta)_{-i, i} \Sigma(\theta)^{-1}_{i, i} (x_i - \mu (\theta)_i) (\#eq:wood3)
$$
The proposed modification has two parts:

1. Use the numerically exact $\mu(x_i, \theta)$ rather than an approximation (as in simplified Laplace)
2. An approximation to the required Hessian

@@

1. Compute the Cholesky factor of $Q_0 := Q_{-i, -i}$ by update of the Cholesky factor of $Q$
2. For each $x_i$ in a grid of evaluation points (how does one chose this grid?) repeat the following steps a-e)
  a) Use Newton's method with fixed Hessian $Q_{-i, -i}$ to find $\mu(x_i)$ starting from \@ref(eq:wood3)
  b) Compute a set of $J$ steps $\{\Delta_j\}$
  c) For $j = 1, \ldots, J - 1$ compute
  $$
  q = Q_0 \Delta_j + u_j \mathcal{D}_{2j}u_j^\top \Delta_j
  $$
  and
  $$
  g = \Delta_x \log p(\mu(x_i) + \Delta_j^i, y, \theta).
  $$
  Then compute the matrix
  $$
  u_{j + 1} = \{q(\Delta_j^\top j)^{-1/2}, g_{-i}(\Delta_j^\top g_{-i})^{-1/2}, u_j\}.
  $$
  d) Compute the determinant approximation...
  e) Compute $\tilde p(x_i \, | \, \theta, y) = \ldots$
3. Renormalise $\tilde p(x_i \, | \, \theta, y)$

@@

| Description | Here | Wood (2019) notation | Notes |
|-------------|:--------------:|:--------------------:|:---------|
| Random effects | $x$ | $\beta$ | Stringer (2021) use $w$
| Random effects which maximise (the / some) objective for given $\theta$ | $\mu (\theta)$ | $\hat \beta$ | Wood omits dependence on $\theta$ |
| Random effects which maximise (the / some) objective for given $\theta$, subject to $x_i$ being fixed | $(x_i, \mu(x_i, \theta))$ | $\tilde \beta$ | We have $\mu(x_i, \theta))$ having dimension $n - 1$ |
| Hessian / precision matrix of the negative log-likelihood with respect to $x$ at $\mu(\theta)$ | $Q(\theta)$ | $H$ | Unsure if it's preferable to use Hessian or precision notation here |

>>>>

### Calculating $p_\text{LA}(\hat \theta \, | \, y)$ with `aghq`

```{r}
# h$he <- function(theta) numDeriv::jacobian(h$gr, theta, method = "Richardson")
# quad <- aghq::aghq(ff = h, k = 1, startingvalue = h$par)
```

@@

In Section \@ref(full-laplace) we directly calculate the Laplace approximation to $\int p(x, y, \theta) \text{d} \theta_{-i}$.
Suppose that
$$
x \sim \mathcal{N}(\mu(\theta), Q(\theta)^{-1})
$$
then by the conditional distributions of a multivariate Gaussian distribution $x_{-i} \, | \, x_i$ is Gaussian with mean
$$
\mu(\theta)_{-i} + \Sigma(\theta)_{-i, i} \Sigma(\theta)^{-1}_{i, i} (x_i - \mu (\theta)_i) (\#eq:conditionalmean)
$$
and precision matrix
$$
Q(\theta)_{-i, -i}
$$

@@

1. Compute the Cholesky factor of $Q_0 := Q_{-i, -i}$ by update of the Cholesky factor of $Q$
2. For each $x_i$ in a grid of evaluation points (how does one chose this grid?) repeat the following steps a-e)
  a) Use Newton's method with fixed Hessian $Q_{-i, -i}$ to find $\mu(x_i)$ starting from \@ref(eq:conditionalmean)
  b) Compute a set of $J$ steps $\{\Delta_j\}$
  c) For $j = 1, \ldots, J - 1$ compute
  $$
  q = Q_0 \Delta_j + u_j \mathcal{D}_{2j}u_j^\top \Delta_j
  $$
  and
  $$
  g = \Delta_x \log p(\mu(x_i) + \Delta_j^i, y, \theta).
  $$
  Then compute the matrix
  $$
  u_{j + 1} = \{q(\Delta_j^\top j)^{-1/2}, g_{-i}(\Delta_j^\top g_{-i})^{-1/2}, u_j\}.
  $$
  d) Compute the determinant approximation...
  e) Compute $\tilde p(x_i \, | \, \theta, y) = \ldots$
3. Renormalise $\tilde p(x_i \, | \, \theta, y)$

@@

| Description | Here          | Wood (2019) notation | Notes    |
|:------------|:--------------|:---------------------|:---------|
| Random effects | $x$        | $\beta$              | Stringer (2021) use $w$
| Random effects which maximise (the / some) objective for given $\theta$ | $\mu (\theta)$ | $\hat \beta$ | Wood omits dependence on $\theta$ |
| Random effects which maximise (the / some) objective for given $\theta$, subject to $x_i$ being fixed | $(x_i, \mu(x_i, \theta))$ | $\tilde \beta$ | We have $\mu(x_i, \theta))$ having dimension $n - 1$ |
| Hessian / precision matrix of the negative log-likelihood with respect to $x$ at $\mu(\theta)$ | $Q(\theta)$ | $H$ | Unsure if it's preferable to use Hessian or precision notation here |
